### 2025-03-09 codes_original_submission/GRAPHICALMODEL/OlderFiles/horizonTask_graphicalModel_v3.tex
u

\documentclass[12pt]{article}
\usepackage{pst-all}
\usepackage{com.braju.graphicalmodels}
%\usepackage[pass,paperwidth=8.5in,paperheight=11in]{geometry}
\usepackage{ifpdf}
\ifpdf
  \pdfpaperheight=6in
  \pdfpaperwidth=9.5in
\else
  \special{papersize=9.3in,5in}
\fi
\catcode`\@=11%
\pagestyle{empty}
%\setlength{\textheight}{9.3in}
%\setlength{\textwidth}{7in}
%\setlength{\footskip}{0.5in}
%\setlength{\topmargin}{-0.5in}
%\setlength{\headheight}{0.2in}
%\setlength{\headsep}{0in}
%\setlength{\parindent}{1pc}
%\setlength{\oddsidemargin}{-0.25in}
%\setlength{\evensidemargin}{-0.25in}
\begin{document}
\TeXtoEPS
\psset{unit=14mm,arrowscale=1.5}
\SpecialCoor

@@

\begin{pspicture}(0.5,2)(13,9)
\showgrid

@@

% dm and dI
\rput(4,4){\GM@node[observed=true,observedColor=lightgray,nodeSize=12mm]{dm}}\GM@label[offset=-5.7mm]{dm}{$\Delta R_{nst}$}
\rput(6,4){\GM@node[query=true,observed=true,observedColor=lightgray,nodeSize=12mm]{dI}}\GM@label[offset=-5mm]{dI}{$\Delta I_{nst}$}

@@

% hyperparameters
\rput(0.8,10){\GM@node[nodeSize=12mm]{muA}}\GM@label[offset=-2mm]{muA}{$\mu^A_{n}$}
\rput(1.75,10){\GM@node[nodeSize=12mm]{sigmaA}}\GM@label[offset=-2mm]{sigmaA}{$\sigma^A_{n}$}
\rput(2.7,10){\GM@node[nodeSize=12mm]{betaA}}\GM@label[offset=-2mm]{betaA}{$\beta^A_{n}$}

\rput(4.05,10){\GM@node[nodeSize=12mm]{mub}}\GM@label[offset=-2mm]{mub}{$\mu^B_{n}$}
\rput(5,10){\GM@node[nodeSize=12mm]{sigmab}}\GM@label[offset=-2mm]{sigmab}{$\sigma^B_{n}$}
\rput(5.95,10){\GM@node[nodeSize=12mm]{betab}}\GM@label[offset=-2mm]{betab}{$\beta^B_{n}$}

\rput(7.3,10){\GM@node[nodeSize=12mm]{kSigma}}\GM@label[offset=-2mm]{kSigma}{$k^\sigma_{n}$}
\rput(8.25,10){\GM@node[nodeSize=12mm]{lambdaSigma}}\GM@label[offset=-2mm]{lambdaSigma}{$\lambda^\sigma_{n}$}
\rput(9.2,10){\GM@node[nodeSize=12mm]{betaSigma}}\GM@label[offset=-2mm]{betaSigma}{$\beta^\sigma_{n}$}

% blink rate
\rput(-0.5,6){\GM@node[observed=true,observedColor=lightgray,nodeSize=12mm]{BR}}\GM@label[offset=-4mm]{BR}{$BR_{s}$}

@@

% 3. Arrows
%%%%%%%%%%%
%
\ncline[arrows=->]{dm}{c}
\ncline[arrows=->]{dI}{c}

@@

\ncline[arrows=->]{muA}{A}
\ncline[arrows=->]{sigmaA}{A}
\ncline[arrows=->]{betaA}{A}

\ncline[arrows=->]{kSigma}{sigma}
\ncline[arrows=->]{lambdaSigma}{sigma}
\ncline[arrows=->]{betaSigma}{sigma}

\ncline[arrows=->]{mub}{b}
\ncline[arrows=->]{sigmab}{b}
\ncline[arrows=->]{betab}{b}

\ncline[arrows=->]{BR}{A}
\ncline[arrows=->]{BR}{b}
\ncline[arrows=->]{BR}{sigma}

@@

\rput(3.25,3){\GM@plate{3.5}{4}{game $t=1$:$T$   }}
\rput(-1.25,2.5){\GM@plate{9.5}{6.5}{subject $s=1$:$S$   }}
\rput(0.25,2){\GM@plate{9.5}{8.75}{condition $n=1$:$N$   }}
%\rput(1,1.5){\GM@plate{10}{10}{$u\in\left\{ [1\mbox{ }3], [2\mbox{ }2]\right\}$   }}

@@

% priors
\rput(10,10.6){\pnode{priors}}\GM@label{priors}{Priors}
\rput(10,10.05){\pnode{muA}}\GM@label{muA}{$\mu^A_{n} \sim \mbox{Gaussian}(0, 1000)$}
\rput(10,9.6){\pnode{sigmaA}}\GM@label{sigmaA}{$\sigma^A_{n} \sim \mbox{Gamma}(0.001, 0.001)$}
\rput(10,9.15){\pnode{betaA}}\GM@label{betaA}{$\beta^A_{n} \sim \mbox{Gaussian}(0, 1000)$}

\rput(10,8.55){\pnode{mub}}\GM@label{mub}{$\mu^B_{n} \sim \mbox{Gaussian}(0, 1000)$}
\rput(10,8.1){\pnode{sigmab}}\GM@label{sigmab}{$\sigma^B_{n} \sim \mbox{Gamma}(0.001, 0.001)$}
\rput(10,7.65){\pnode{betaB}}\GM@label{betaB}{$\beta^B_{n} \sim \mbox{Gaussian}(0, 1000)$}

\rput(10,7.05){\pnode{kSigma}}\GM@label{kSigma}{$k^\sigma_{n} \sim \mbox{Exponential}(0.001)$}
\rput(10,6.6){\pnode{lambdaSigma}}\GM@label{lambdaSigma}{$\lambda^\sigma_{n} \sim \mbox{Exponential}(0.001)$}
\rput(10,6.15){\pnode{betaSigma}}\GM@label{betaSigma}{$\beta^\sigma_{n} \sim \mbox{Gaussian}(0, 1000)$}

% subject level params
\rput(10,5.5){\pnode{subpars}}\GM@label{subpars}{Subject specific parameters}
\rput(10,5){\pnode{A}}\GM@label{A}{$A_{ns} \sim \mbox{Gaussian}(\mu^A_{n}, \sigma^A_{n}) + \beta_n^A BR_s$}
\rput(10,4.5){\pnode{b}}\GM@label{b}{$B_{ns} \sim \mbox{Gaussian}(\mu^B_{n}, \sigma^B_{n})+ \beta_n^B BR_s$}
\rput(10,4){\pnode{sigma}}\GM@label{sigma}{$\sigma_{ns} \sim \mbox{Gamma}(k^\sigma_{n}, \lambda^\sigma_{n})+ \beta_n^\sigma BR_s$}

@@

\rput(10,3.4){\pnode{choices}}\GM@label{choices}{Observed choices}
\rput(10,2.9){\pnode{p}}
\GM@label{p}{$p_{nst} \leftarrow
\left[1+\exp\left( \frac{\Delta R_{nst}+A_{ns}\Delta I_{nst} + B_{ns}}{\sigma_{ns}} \right)\right]^{-1} $}
\rput(10,2.3){\pnode{c}}
\GM@label{c}{$c_{nst} \sim \mbox{Bernoulli}
\left( p_{nst} \right)$}

>>>>

\documentclass[12pt]{article}
\usepackage{pst-all}
\usepackage{com.braju.graphicalmodels}
%\usepackage[pass,paperwidth=8.5in,paperheight=11in]{geometry}
\usepackage{ifpdf}
\ifpdf
  \pdfpaperheight=6in
  \pdfpaperwidth=9.5in
\else
  \special{papersize=7.6in,5in}
\fi
\catcode`\@=11%
\pagestyle{empty}
%\setlength{\textheight}{9.3in}
%\setlength{\textwidth}{7in}
%\setlength{\footskip}{0.5in}
%\setlength{\topmargin}{-0.5in}
%\setlength{\headheight}{0.2in}
%\setlength{\headsep}{0in}
%\setlength{\parindent}{1pc}
%\setlength{\oddsidemargin}{-0.25in}
%\setlength{\evensidemargin}{-0.25in}
\begin{document}
\TeXtoEPS
\psset{unit=14mm,arrowscale=1.5}
\SpecialCoor

@@

\begin{pspicture}(2.95,2)(13,9)
%\showgrid

@@

% dm and dI
\rput(3,4){\GM@node[observed=true,observedColor=lightgray,nodeSize=12mm]{dm}}\GM@label[offset=-5.7mm]{dm}{$\Delta R_{nst}$}
\rput(5,4){\GM@node[query=true,observed=true,observedColor=lightgray,nodeSize=12mm]{dI}}\GM@label[offset=-5mm]{dI}{$\Delta I_{nst}$}
\rput(7,4){\GM@node[query=true,observed=true,observedColor=lightgray,nodeSize=12mm]{dl}}\GM@label[offset=-5.7mm]{dl}{$\Delta l_{nst}$}

@@

% hyperparameters
\rput(2,10){\GM@node[nodeSize=12mm]{muA}}\GM@label[offset=-2mm]{muA}{$\mu^A_{n}$}
\rput(3,10){\GM@node[nodeSize=12mm]{sigmaA}}\GM@label[offset=-2mm]{sigmaA}{$\sigma^A_{n}$}

\rput(4.5,10){\GM@node[nodeSize=12mm]{mub}}\GM@label[offset=-2mm]{mub}{$\mu^B_{n}$}
\rput(5.5,10){\GM@node[nodeSize=12mm]{sigmab}}\GM@label[offset=-2mm]{sigmab}{$\sigma^B_{n}$}

\rput(7,10){\GM@node[nodeSize=12mm]{kSigma}}\GM@label[offset=-2mm]{kSigma}{$k^\sigma_{n}$}
\rput(8,10){\GM@node[nodeSize=12mm]{lambdaSigma}}\GM@label[offset=-2mm]{lambdaSigma}{$\lambda^\sigma_{n}$}

@@

% 3. Arrows
%%%%%%%%%%%
%
\ncline[arrows=->]{dm}{c}
\ncline[arrows=->]{dI}{c}
\ncline[arrows=->]{dl}{c}

@@

\ncline[arrows=->]{muA}{A}
\ncline[arrows=->]{sigmaA}{A}

\ncline[arrows=->]{kSigma}{sigma}
\ncline[arrows=->]{lambdaSigma}{sigma}

\ncline[arrows=->]{mub}{b}
\ncline[arrows=->]{sigmab}{b}

@@

\rput(2.25,3){\GM@plate{5.5}{4}{game $g=1$:$G$   }}
\rput(1.75,2.5){\GM@plate{6.5}{6.5}{subject $s=1$:$S$   }}
\rput(1.25,2){\GM@plate{7.5}{8.75}{condition $n=1$:$N$   }}
%\rput(1,1.5){\GM@plate{10}{10}{$u\in\left\{ [1\mbox{ }3], [2\mbox{ }2]\right\}$   }}

@@

% priors
\rput(9,10.5){\pnode{priors}}\GM@label{priors}{Priors}
\rput(9,10){\pnode{muA}}\GM@label{muA}{$\mu^A_{n} \sim \mbox{Gaussian}(0, 1000)$}
\rput(9,9.5){\pnode{sigmaA}}\GM@label{sigmaA}{$\sigma^A_{n} \sim \mbox{Gamma}(0.001, 0.001)$}

\rput(9,9){\pnode{mub}}\GM@label{mub}{$\mu^B_{n} \sim \mbox{Gaussian}(0, 1000)$}
\rput(9,8.5){\pnode{sigmab}}\GM@label{sigmab}{$\sigma^B_{n} \sim \mbox{Gamma}(0.001, 0.001)$}

\rput(9,8){\pnode{kSigma}}\GM@label{kSigma}{$k^\sigma_{n} \sim \mbox{Exponential}(0.001)$}
\rput(9,7.5){\pnode{lambdaSigma}}\GM@label{lambdaSigma}{$\lambda^\sigma_{n} \sim \mbox{Exponential}(0.001)$}

% subject level params
\rput(9,6.5){\pnode{subpars}}\GM@label{subpars}{Subject specific parameters}
\rput(9,6){\pnode{A}}\GM@label{A}{$A_{ns} \sim \mbox{Gaussian}(\mu^A_{n}, \sigma^A_{n})$}
\rput(9,5.5){\pnode{b}}\GM@label{b}{$B_{ns} \sim \mbox{Gaussian}(\mu^B_{n}, \sigma^B_{n})$}
\rput(9,5){\pnode{sigma}}\GM@label{sigma}{$\sigma_{ns} \sim \mbox{Gamma}(k^\sigma_{n}, \lambda^\sigma_{n})$}

@@

\rput(9,4){\pnode{choices}}\GM@label{choices}{Observed choices}
\rput(9,3.5){\pnode{p}}
\GM@label{p}{$p_{nst} \leftarrow
\left[1+\exp\left( \frac{\Delta R_{nst}+A_{ns}\Delta I_{nst} + B_{ns}\Delta l_{nst}}{\sigma_{ns}} \right)\right]^{-1} $}
\rput(9,2.9){\pnode{c}}
\GM@label{c}{$c_{nst} \sim \mbox{Bernoulli}
\left( p_{nst} \right)$}
